\section{EPR Pairs and Entanglement}
The EPR pairs have a special significance in quantum computing for example in teleportation and super-dense coding. The reason of their special significance is that when a measurement is performed on a single bit, we get the information of the both the bits of the collapsed state. The EPR pairs are also called Bell states.
\par
The EPR pairs are given by:
$$\ket{\beta_{00}} = \frac{\ket{00}+\ket{11}}{\sqrt{2}}  $$
$$\ket{\beta_{01}} = \frac{\ket{01}+\ket{10}}{\sqrt{2}}  $$
$$\ket{\beta_{10}} = \frac{\ket{00}-\ket{11}}{\sqrt{2}}  $$
$$\ket{\beta_{11}} = \frac{\ket{01}-\ket{10}}{\sqrt{2}}  $$
An easier way to remember this is:
$$\ket{\beta_{xy}} = \frac{\ket{0,y} + (-1)^x \ket{1,1 -y}}{\sqrt{2}}$$

This also explains a way of making them, by passing of $\ket{x}$
through a Hadmard gate , followed by a CNOT gate with $\ket{y}$ as the target bit.
\subsection{Teleportation}
Say Alice and Bob share an EPR pair where in , Alice possess the first qubit of the pair while Bob possess the second qubit. The task of quantum teleportation implies, given an unknown $\ket{\psi}$ in possession of Alice , she must teleport it to Bob , given that she can convey only classical bits of information to him. She can do so in the following way:\\
Lets say the EPR pair shared by Alice and Bob is
$$\ket{\beta_{01}} = \frac{\ket{01}+\ket{10}}{\sqrt{2}}  $$
And the unknown state $\ket{\psi}$ be represented by 
	$$\ket{\psi} = a\ket{0} + b\ket{1}$$
Then a circuit describe by Figure 2 is essentially what we need.
Proof of the teleportation circuit:\\  
The state of the sytem just before any computation is given by:
$$\ket{\psi} = \frac{a\ket{0}(\ket{01}+\ket{10}) + b\ket{1}(\ket{01}+\ket{10})}{\sqrt{2}}$$

\subsection{Super Dense Coding}
Suppose Alice wants to share two bits of information to Bob , given that they are distant away while they share an EPR pair and Alice can interact only with qubit. Is this possible?\\
The answer to the question is infact Yes.\\Alice does so in the following way:\\
\newline
Suppose the state/ EPR shared by Alice and Bob is 
$$\ket{\psi} = \frac{\ket{00}+\ket{11}}{\sqrt{2}}$$
where Alice is in possession of the first bit while Bob is in the possession of the second bit.\\
Now if Alice wishes to send the bit string '00', then she does nothing to her bit, if she wishes to send '01', then she applies a phase shift, Z gate to her bit.If she wishes to send '10', then she just applies the bit flip X gate, anf finally if she wishes to send '11' she applies X gate followed by Z gate to her bit.The result of all this can in fact be summaried as:
$$00: \ket{\psi} \to \ket{\beta_{00}}$$
$$01: \ket{\psi} \to \ket{\beta_{01}}$$
$$10: \ket{\psi} \to \ket{\beta_{10}}$$
$$11: \ket{\psi} \to \ket{\beta_{11}}$$
Indeed, we have the 4 EPR pairs. Now if Alice sends her qubit to Bob then Bob has possession of both the qubits. Notice that EPR pairs form an orthonormal basis of the two-qubit space. Hence by making a measurement in the Bell basis, Bob can identify the which bit string was sent by Alice.